\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{color}
\usepackage[total={6in,8in}]{geometry}
\usepackage{amsthm}

\usepackage{enumitem}
\usepackage{centernot}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\sn}{\mathfrak{S}}
\newcommand{\ve}{\varepsilon}
\setlength{\parindent}{1cm}


\author{Marika Swanberg}

\begin{document}
Marika Swanberg and Jillian James, Homework 3, \today
\bigskip 

\section{Laura and Lucas}
We had no compilation or linking errors with their code. It looks like they failed some of our tests that look at memused because they do not decrement memused upon deleting entries. Another problem that is probably causing most of the other fails is in the way that they store the size of the value. Their code stores that \texttt{size = sizeof(val)}, but \texttt{val} is a pointer, not the actual \textit{value} pointed to by the void pointer they are storing in the map. We had the same issue, so we are familiar with it.

\section{Sierra and Mercy}
We had no compilation or linking errors. Only one couple of our tests failed, where we try to \texttt{get()} an entry that has been deleted from the cache. Based on the feedback from Catch2, it looks like their code throws some kind of exception in this case because the code is working with a nullptr. This situation is not defined in the API so it is not necessarily wrong that the code throws an exception. However, we looked at their source code and could not find why this exception was thrown; it looks like they are handling the case we were trying to test in their \texttt{get()} function, so it's hard to say what is going on. Therefore we decided to make note of this.

\section{Henry and Noah}
We spent about an hour reading their README.md file to try to figure out how to compile their code in a way that we could incorporate our test file. Although they had a makefule there was no documentation on how to use this in genral or how to incorporate our own test file for testing purposes. Unfortunately, we were unsuccessful and ultimately had to give up trying to sift through dozens of files in different folders and their different eviction implementations.

\section{Grant and Naomi}
There were no compilation errors but the compilor gave some warnings when run with error flags: -Wall -Wextra -pedantic. The code passed all but one test. It failed the test in which we evict multiple elements from the cache in order to include a new, larger value. You need your if (memused_ > maxmem) check to be in loop, we also had this error before so we are familiar with it. 

\end{document}